% Template to be used while publishing    
% a scientific work (PhD Thesis etc.)
% at the EDOC-Server of HU-Berlin                      
%    developed 2003-2008 by
% AG Elektronisches Publizieren, 
% Computer- und Medienservice,
% Humboldt-Universitaet zu Berlin
%    with friendly support of
% TeX-Stammtisch in Berlin     

% $Revision: 19 $
% $HeadURL: svn+ssh://ryckojox@svn.cms.hu-berlin.de/svn/projects/epub/latex/hudiss/mustermann.tex $
% $Date: 2009-07-03 15:49:19 +0200 (ptk, 03 lip 2009) $
% $Author$
% $Id: mustermann.tex 19 2009-07-03 13:49:19Z ryckojox $
                             
% Questions, comments, support:
%    edoc-latex@cms.hu-berlin.de    

% Documentation and information about the conditions of a publication:
%    http://edoc.hu-berlin.de/e_autoren/latex          

% Upload:
%    https://edoc.hu-berlin.de/cgi/dokupload/dokupload.cgi

\documentclass[openright,twoside,headsepline,bibtotoc]{scrbook}[2007/12/24]

% The following package is necessary.
% To change the default options of the packages, use the key=value interface.
% See the documentation for details.
% If you need to use any special characters or LaTeX-commands 
% within the options, use \hudisssetup{} after loading this package,
% otherwise they will NOT work correctly.
\usepackage[
    inputenc=applemac, % default - latin1
    %fontset=palatino, % other possible parameters: lmodern, times, palatino
    natbib={round,authoryear}, %include to use the natbib-package % sort sortiert nach Name
    % jurabib={}, %include to use the jurabib-package
    % apacite={}, %include to use the apacite-package
    hints=false, % set to 'false' for submission
    checktabu=false, % set to 'false' for submission
    draft=false, % set to 'false' for submission
    qserie=false
 ]{hudiss}

%\usepackage{layouts} % nur für Ausgabe der Textbreite
% Breite hier: B=14,6979 cm. Ergibt H=8,3988 cm für 7/4 Verhältnis
% für kleine Bilder nehmen wir 6.5/4: BxH=8.819x5.427

                
\hudisssetup{%
    titlepagefont={\Large\sffamily} % Use to change the titlepage font
}

% Fill out all the metadata here:
\hudissmetadata{%
    authorprefix={Dipl.-Phys.}, % e.g. Dipl.-Inf.
    authorfirstname={Hartmut}, % first name
    authorsurname={Lentz}, % surname
    authorsuffix={}, % e.g. Ph.D.
    authoradd={geboren am 23.\,10.~1980 in Siegen}, % date and place of birth
    doctitle={Paths for Epidemics\\ in Static and Temporal Networks}, % title of the thesis
    %docsubtitle={for one euro}, % subtitle of the thesis
    % docsubject={Analysis of complex networks}, % subject of the thesis (used in the properties of the pdf-document)
    approvala={..........................}, % approvals: a-e
    approvalb={..........................},
    approvalc={..........................},
    % approvald={},
    % approvale={},
    degree={doctor rerum naturalium\\(Dr. rer. nat.)}, % e.g. Dr. Rer. Nat.
    subject={Physik}, % e.g. Informatik
    faculty={Mathematisch-Wissenschaftlichen Fakultät I}, % in Dativ/Genitiv! e.g. Mathematisch-Wissenschaftlichen Fakult\"at II
    university={Humboldt-Universität zu Berlin}, % e.g. Humboldt-Universit\"at zu Berlin
    dean={Prof. Stefan Hecht, PhD}, % dean of the faculty
    president={Prof. Dr. Jan-Hendrik Olbertz}, % president of the university
    %datesubmitted={..........................}, % the date of the submission
    dateexam={..........................}, % the date of your last exam
    keywordsen={Complex Network, Epidemiology, Temporal Network }, % english keywords comma separated
    keywordsde={Komplexes Netzwerk, Epidemiologie, zeitabhängiges Netzwerk} % german keywords comma separated
}

% If you wish to load any further packages, 
% make any own adjustments (e. g. for the package fancyhdr)
% or define any own commands
% put ALL of them in the following file:
\input{adjustment.tex}


% The order of the parts in the document is only our suggestion,
% you can change it, if you wish.
% Don't put any other text between those commands.
% Do not remove the \*matter macros.
% Use standard macros to include new chapters.



%%%%%    \includeonly{chapters/Part1/01-Introtext}
% DIV is 10, BCOR is 0mm
\begin{document}
\selectlanguage{english}

\chapter*{List of publications}
\thispagestyle{empty}
\begin{enumerate}
 \item \textbf{H. H. K. Lentz}, T. Selhorst and I. M. Sokolov\\
 \textit{Unfolding Accessibility provides a Macroscopic Approach to Temporal Networks}\\
  Physical Review Letters 110: 118701 (2013).

 \item M. Konschake, \textbf{H. H. K. Lentz}, F. J. Conraths, P. Hoevel and T. Selhorst\\
  \textit{On the Robustness of In- and Out-Components in a Temporal Network}\\
  PLoS ONE 8(2): e55223 (2013).

 \item \textbf{H. H. K. Lentz}, T. Selhorst and I. M. Sokolov\\
  \textit{Spread of infectious diseases in directed and modular metapopulation networks}\\
  Physical Review E 85: 066111 (2012).

  \item \textbf{H. H. K. Lentz},  M. Konschake, K. Teske, M. Kasper, B. Rother, R. Carmanns, B. Petersen, F. J. Conraths and T. Selhorst \\
   \textit{Trade communities and their spatial patterns in the German pork production network}\\
  Preventive Veterinary Medicine 98: 176--181 (2011).

  \item \textbf{H. Lentz},  M. Kasper and T. Selhorst \\
   \textit{Beschreibung des Handels mit Rindern in Deutschland mittels Netzwerkanalyse -- Ergebnisse von Voruntersuchungen}\\
  Berliner und Münchener Tierärztliche Wochenschrift 122: 193--198 (2009).

\end{enumerate}%\clearpage
%%%% CV %%%%%
\chapter*{Curriculum Vitae}
\thispagestyle{empty}

\begin{cv}{~}
  
\begin{cvlist}{\color{Steel}{Personal information}}
  \item Dipl.-Phys. Hartmut Lentz
    \item born in Siegen, October 23rd 1980\\
	Nationality: German
    \item[contact] Friedrich-Loeffler-Institute\\
    Institute for Epidemiology\\
    Seestr. 55\\
    106868 Wusterhausen, Germany
 % \item +49-(30)~2093-7750\\
   \item hartmut.lentz@fli.bund.de	

\end{cvlist}
%\vspace{0.1cm}
 % \noindent\hrulefill

  \begin{cvlist}{\color{Steel}{Education and job history}}
  \item[since 04/2008] Research assistant, Friedrich-Loeffler-Institute (Federal Research Institute for Animal Health), Working group Theoretical Epidemiology
   \item[since 04/2008] Ph.D. student, Humboldt-University of Berlin, Department of
Physics, Statistical Physics and Nonlinear Dynamics, Topic: \emph{Spread of infectious diseases in complex networks}.
  \item[10/2007] Diploma in theoretical physics at Department of Physics, Technical University Berlin, Topic: \emph{Rotierende Wellenmuster in erregbaren Medien}, (graduated with honors).
  \item[10/2007--04/2008] Research assistant, Technical University Berlin
  \item[10/2001--10-2007] Physics study at Freie University Berlin and Technical University Berlin
  \item[06/2001] Abitur, Evangelisches Gymnasium Siegen
  \end{cvlist}

  \date{}
\end{cv}

\vspace{1\baselineskip}
\noindent Berlin, \today   %\newline

\par\hspace{8cm}  ( \authorfirstname \authorsurname)





\end{document}
