%\cleardoublepage
%\thispagestyle{plain}
\chapter*{Acknowledgement}
First of all, I would like to thank Thomas Selhorst for his endless support and for giving me the opportunity to work independently on an exciting topic.
Furthermore, I thank Igor Sokolov for the many fruitful discussions and the development of new ideas, in particular our different approaches for the formulation of accessibility.

This thesis has been developed at two different locations: the Humboldt-University of Berlin and the Friedrich-Loeffler-Institute in Wusterhausen.
Concerning the physical side of my work, I would like to thank Federico Camboni for discussions and calculations, particularly about matrices, and Vitaly Belik for sharing his ideas and knowledge about networks and epidemiology with me.
I thank Mario Konschake for many fruitful discussions and for helping to increase my computer skills significantly.

I thank my colleagues from the Friedrich-Loeffler-Institute for guiding the focus of my research so that I could address some real-world problems.
In particular, Jšrn Gethmann, Christoph Staubach and Matthias Kramer provided a realistic picture of disease management.
%Additionally, I thank Maria Kasper for listening my thoughts about vectors and ice cream cones.
I would like to thank Hans Thulke for his great interest in my work and discussions about networks and automata.

I would also like to thank Tim Baldsiefen, Christian Schmeltzer for helping me with the manuscript.
Finally, I thank my family for their support during the last years.
I thank Sarah for bearing with me in phases of scientific frustration and hope that I'll have more time to spend with my daughters Laurena and Thalina in the future.

